Building Sustainable Software - The CSDMS Approach

### 2014-07-14 hutton_et_al_2014_wssspe.tex
Fixed spelling mistake.

\csdms{}, The Community Surface Dynamics Modeling System, is an NSF funded
project whose focus is to aid a diverse community of earth and ocean system
model \emph{users} and \emph{developers} to use and create robust software
quickly.  To this end, \csdms{} develops, integrates, archives and disseminates
earth-system models and tools to an international (67 country) community
with the goal of building the set of tools necessary to model the
earth system. Modelers use \csdms{} for access to hundreds of open
source surface-dynamics models and tools, as well as model metadata. Such a
model repository increases model transparency and helps eliminate
duplication by presenting the current state of modeling efforts.
To increase software sustainability, composability and interoperability,
\csdms{} promotes standards that define common modeling interfaces, semantic
mediation between models, and model metadata. Through online resources and
workshops, \csdms{} promotes software engineering best practices, which are
unfamiliar to many developers within our modeling community. For example,
version control, unit testing, continious integration, test-driven
development, and well-written \emph{clean code} are all topics of the
educational mission of \csdms{}.

>>>>

\csdms{}, The Community Surface Dynamics Modeling System, is an NSF funded
project whose focus is to aid a diverse community of earth and ocean system
model \emph{users} and \emph{developers} to use and create robust software
quickly.  To this end, \csdms{} develops, integrates, archives and disseminates
earth-system models and tools to an international (67 country) community
with the goal of building the set of tools necessary to model the
earth system. Modelers use \csdms{} for access to hundreds of open
source surface-dynamics models and tools, as well as model metadata. Such a
model repository increases model transparency and helps eliminate
duplication by presenting the current state of modeling efforts.
To increase software sustainability, composability and interoperability,
\csdms{} promotes standards that define common modeling interfaces, semantic
mediation between models, and model metadata. Through online resources and
workshops, \csdms{} promotes software engineering best practices, which are
unfamiliar to many developers within our modeling community. For example,
version control, unit testing, continuous integration, test-driven
development, and well-written \emph{clean code} are all topics of the
educational mission of \csdms{}.
